Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-02-27 paper/EDA.qmd
box plot for result before and after the game

# Ensure the table prints correctly
print(summary_table)

# Display formatted table using kable
kable(summary_table, 
      caption = "Summary Statistics for Quantitative Variables",
      align = "c") |> print()
```

@@

@@

>>>>

kable(summary_table, format = "latex", booktabs = TRUE, caption = "Summary Statistics for Quantitative Variables") 
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false

# Count and percentage for Drug
drug_counts <- table(clean_data$drug)
drug_percentages <- prop.table(drug_counts) * 100
drug_summary <- data.frame(Drug = names(drug_counts), Count = as.numeric(drug_counts), Percentage = round(as.numeric(drug_percentages), 2))
colnames(drug_summary) <- c("Drug", "Count", "Percentage")

# Count and percentage for Dosage Level
dosage_counts <- table(clean_data$dosage_level)
dosage_percentages <- prop.table(dosage_counts) * 100
dosage_summary <- data.frame(Dosage = names(dosage_counts), Count = as.numeric(dosage_counts), Percentage = round(as.numeric(dosage_percentages), 2))

# Count and percentage for Location
location_counts <- table(clean_data$location)
location_percentages <- prop.table(location_counts) * 100
location_summary <- data.frame(Location = names(location_counts), Count = as.numeric(location_counts), Percentage = round(as.numeric(location_percentages), 2))

# Count and percentage for Age Group
age_counts <- table(clean_data$age_group)
age_percentages <- prop.table(age_counts) * 100
age_summary <- data.frame(Age_Group = names(age_counts), Count = as.numeric(age_counts), Percentage = round(as.numeric(age_percentages), 2))

# Print tables
kable(drug_summary, format = "latex", booktabs = TRUE, caption = "Summary of Drug Types")

kable(dosage_summary, format = "latex", booktabs = TRUE, caption = "Summary of Dosage Levels")

kable(location_summary, format = "latex", booktabs = TRUE, caption = "Summary of Locations")

kable(age_summary, format = "latex", booktabs = TRUE, caption = "Summary of Age Groups") 
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.width: 9
#| fig.height: 8
#| dpi: 300
#| fig-cap: "Boxplot of Game Scores Before and After by Drug"

library(ggplot2)
library(patchwork)  # For combining plots

# Capitalize legend labels
clean_data$drug <- factor(clean_data$drug, labels = c("Aspirin", "Paracetamol", "Placebo", "Tramadol"))

# Create first boxplot
p1 <- ggplot(clean_data, aes(x = drug, y = game_before, fill = drug)) + 
  geom_boxplot() +
  labs(title = "Game Scores Before Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
  theme_minimal()

# Create second boxplot
p2 <- ggplot(clean_data, aes(x = drug, y = game_after, fill = drug)) + 
  geom_boxplot() +
  labs(title = "Game Scores After Treatment", x = "Drug Type", y = "Game Score", fill = "Drug") +
  theme_minimal()

# Combine both plots with a single caption
p1 / p2 + plot_annotation()
